Epilepsy example

### 2022-11-07 src/epil/epil.Rmd
Laplace marginal for nu

dat$i <- i

@@

ggplot(pdf_and_cdf, aes(x = theta, y = pdf)) +
  geom_line() +
  theme_minimal() +
  labs(x = "nu[1]", y = "Posterior")
```

>>>>

Create a function to get the Laplace marginal for the $i$th element of $\nu$:

```{r}
xi_laplace_marginal_nu <- function(i, opt_theta, finegrid) {
  dat$i <- i

@@

  return(pdf_and_cdf)
}
```

Now we can compute the Laplace marginal for all `r dat$N * dat$J` indices of $\nu$:

```{r}
fine_grid <- seq(-5, 5, length.out = 1000)

laplace_nu <- lapply(1:(dat$N * dat$J), xi_laplace_marginal_nu, opt_theta = opt_theta, finegrid = fine_grid) %>%
  bind_rows(.id = "index") %>%
  mutate(index = as.numeric(index))
```

There are too many marginals to plot them all, so here's a random subset of size nine:

```{r}
nine_random_indices <- sample(1:(dat$N * dat$J), size = 9)

laplace_nu %>%
  filter(index %in% nine_random_indices) %>%
  ggplot(aes(x = theta, y = pdf)) +
  geom_line() +
  facet_wrap(~index) +
  theme_minimal() +
  labs(x = "nu", y = "Posterior")
```
